---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

1-3
1. inspect the first few lines of the data set: what variables are there? of what type are the variables? what does each variable mean? what do we expect their data range to be?

There is the address of the property as well as pricing information and other housing details.  The variables are num, char, date types.  The variables describe information for each property such as style (numbers for the style), occupancy, sale date/price, and living aspects such as if it has a fireplace, total acres, type of neighborhood, and if it has AC.  We found that most variables are self explanatory for each variables.  Some that we thought were not self explanatory were Style with 12 different levels, occupancy with a range of 5 levels, and neighborhood with 42 levels describing if it was an apt on campus, residential, etc.

2. is there a variable of special interest or focus?
We determined that sale price was a good variable to focus on as well as if the property was on campus or not.

3. start the exploration with the main variable:

what is the range of the variable? draw a histogram for a numeric variable or a bar chart, if the variable is categorical. what is the general pattern? is there anything odd?
follow-up on oddities: see 4

```{r, comment = FALSE}
library(classdata)
ggplot(ames, x = 'Sale Price') + 
  geom_bar()
```

The range is 0 to 20500000 dollars.  After making the histogram for the Sale Price variable, we saw that...

4. pick a variable that might be related to the main variable.

what is the range of that variable? plot. describe the pattern.
what is the relationship to the main variable? plot a scatterplot, boxplot or facetted barcharts (dependening on the types of variables involved). Describe overall pattern, does this variable describe any oddities discovered in 3? Identify/follow-up on any oddities.


Blake
```{r, comment = FALSE}
library(classdata)
```

Dhairya
```{r, comment = FALSE}
hist(ames$`Sale Price`, ames$`TotalLivingArea (sf)`, 
     xlab = "Sale Price", ylab = "TotalLivingArea", 
     main = "Sale Price vs. TotalLivingArea")

This Histogram plots a comparative value between Sale Price (log) and TotalLivingArea (sf). This shows that the TotalLivingArea data is ranging from 100 square feet to 3000 square feet. 
```


Hazer
```{r, comment = FALSE}
#this is a comment
```

